### 2012-02-09 trunk/GUIErrorDetector/paper/introduction.tex
many tweaks

Our static analysis is independent of the call graph construction algorithm.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. GUI applications tend to use reflection, and
in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a good call graph.
To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
also compare its usefulness with existing call graph construction algorithms in
our experiments. Static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To address such limitations, we devise a set
 of error filters to remove likely false positives and redundant warnings.

>>>>

Our static analysis is independent of the call graph construction algorithm.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. GUI applications tend to use reflection, and
in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a good call graph.
To alleviate this problem, we use an algorithm to build reflection-aware call graph, and
also compare its usefulness with existing call graph construction algorithms in
our experiments. Static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To address such limitations, we devise a set
 of error filters to remove likely false positives and redundant warnings.
